# Preface {.unnumbered}

This is a Quarto book.

::: {.callout-note}

To learn more about Quarto books visit <https://quarto.org/docs/books>.

:::

## 环境配置

### VS Code

- 安装 VS Code
- 安装 VS Code 插件
  - R 扩展 - 提供 R 语言支持
  - Quarto 扩展 - 提供 Quarto 功能
  - Markdown 扩展 - 提供 Markdown 格式化快捷方式


### Quarto

Markdown is an easy to read and write text format:

- It's _plain text_ so works well with version control
- It can be **rendered** into HTML, PDF, and more
- Learn more at: <https://quarto.org/docs/authoring/>


### 配置 Python

**设置 `reticulate` 运行的 Python 环境**

根据 quarto 扩展的默认设置，Python 代码将通过 reticulate 来运行。如果没有安装的话需要运行 `install.packages("reticulate")` 安装它。然后使用 `use_condaenv()` 来指定需要的 Conda 环境。

```{r}
#| label: set-python
reticulate::use_condaenv("rmodels")
```


## 环境测试

### Code Cell

Here is a Python code cell:

```{python}
#| label: test-python-interpreter
import os
os.cpu_count()
```

Here is a R code chunk:

```{r}
#| label: test-r-interpreter
plot(cars)
```

### Equation

Use LaTeX to write equations:

$$
\chi' = \sum_{i=1}^n k_i s_i^2
$$

## 项目简介

使用 R/Python 进行模型构建的学习笔记。

- **tidymodels** 软件包的使用 <https://workshops.tidymodels.org>
- 《数据挖掘实战》读书笔记 [@ZhangShuJuWaJueJiYuRYuYanDeShiZhan2021]
- 更多学习材料[@TidymodelsHuanYing; @silgeTidyModeling2022; @silgeSupervisedMachineLearning2023; @robinsonWelcomeTextMining2023; @mcconvilleStatisticalInferenceData2022]

